Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
last revision

FF-Replan replans online, an off-line planner like FF-Replan is RFF
\cite{teichteil2010incremental}. RFF generates policies by determinizing the
given MDP problem, builds partial policies off-line by producing partial
solution plans to the classical planning problem and incrementally aggregating
them into a policy, and using sequential Monte-Carlo simulations to asses the
probability of replanning. Experiments showed that RFF solved more problems
than FF-Replan because it takes the probability a policy has to replan into
account.

PROST \cite{keller2012prost} is a probabilistic planner, which contrary to
\textsc{Gourmand}, is UTC based. It uses techniques to reduce the branching
factor  and limits the search depth so it can focus more on parts that
influence the quality of the resulting policy. Reward lock detection is a
method to detect goals and dead ends in the finite horizon MDP\@. Q-value
Initialization improves the initial start of the UTC algorithm. In the executed
IPPC-11 benchmarks it outperforms other planners such as \textsc{Glutton}.
Later it has been surpassed by \textsc{Gourmand}.

@@

>>>>

While FF-Replan is an online planner, a similar off-line planner is the RFF planner
\cite{teichteil2010incremental}. RFF generates policies by determinizing the
given MDP problem similarly to FF-Replan. It then builds partial policies off-line by producing partial
solution plans to the classical planning problem and incrementally aggregating
them into a policy. Using sequential Monte-Carlo simulations, it estimates the
probability of replanning. Experiments showed that RFF solved more problems
than FF-Replan because it takes the probability a policy has to replan into
account.

PROST \cite{keller2012prost} is a probabilistic planner, which in contrary to
\textsc{Gourmand} is UTC based. It uses techniques to reduce the branching
factor and limits the search depth so it can focus on parts that
influence the quality of the resulting policy. Reward lock detection is a
method to detect goals and dead ends in the finite horizon MDP\@. Q-value
Initialization improves the initial start of the UTC algorithm. In the executed
IPPC-11 benchmarks it outperforms other planners such as \textsc{Glutton}.
Later it has been surpassed by \textsc{Gourmand}.

\todo{connect back to the purpose of the paper}

@@

\todo{we hadden hier al meer voor klaar staan dan alleen dit toch? Het is nog niet echt een aanbeveling}
